Final assignment presentation

### 2022-12-01 summary_final_assingment.Rmd
Update summary_final_assingment.Rmd

p <- ggplot(df, aes(x, y, fill=party)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
  scale_fill_manual(values=colordict) +
  theme_bw()

@@

j <- ggplot(df1, aes(x, y, fill=party)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
  scale_fill_manual(values=colordict2) +
  theme_bw()

@@

-   In general the legilsation appears quite similar, with exceptions limited to specific policy areas and topics
-   Democratic and Republican cooperation across the different congress sessions is highly dependent on the policy area and topic of the bill
-   There are some key actors that enable working across the aisle and are known for bipartisan collaboration

>>>>

p <- ggplot(df, aes(x, y, fill=party)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
  labs(title = "Dimensionality of all summary texts", x = "X", y = "Y",
       fill = "Bill sponsorship", 
       caption = "All bills represented, Democrat are bills with > 0.66 Democrat,
       Republican are bills with > 0.66 Republican, Both are bills in between.") +
  scale_fill_manual(values=colordict) +
  theme_bw()

@@

j <- ggplot(df1, aes(x, y, fill=party)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
    labs(title = "Dimensionality of partisan summary texts", x = "X", y = "Y",
       fill = "Bill sponsorship",
       caption = "Bills with only completely Democrat of 
       Republican sponsorship represented.") +
  scale_fill_manual(values=colordict2) +
  theme_bw()

@@

-   In general the legilsation appears quite similar, with exceptions limited to specific policy areas and topics
-   Democratic and Republican cooperation across the different congress sessions is highly dependent on the policy area and topic of the bill
-   The dimensionality of texts is not systematically different between Democrat and Republican sponsored bills
-   The sentiments of bills sponsored primarily by Democrats or Republicans does not seem correlated with the party in power
-   There are some key actors that enable working across the aisle and are known for bipartisan collaboration
